RAX: A porting complexity evaluation tool for RISC-V

### 2023-10-09 Paper/latex/paper.tex
Add tables.

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{flow-chart.pdf}
  \caption{Flow chart for method to build RAX}
  \label{fig:flow-chart}
  \Description{Flow chart for method to build RAX}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{relationship.pdf}
  \caption{The relationship between score and CC}
  \label{fig:relationship}
  \Description{The relationship between score and CC}
\end{figure}

@@

Continue to collect other factors that may affect the evaluation of porting complexity,and select the following parameters through the Commit analyzer:architecture-related code lines, architecture-related files, and architecture keywords.
The number of architecture-related code lines and files is located using the keywords of X86, ARM, MIPS, RISCV, SPARC and other architectures.
Correlation comparison between Arch\_code and other factors acquired by Commit analyzer,as the picture shows:

@@

@@

>>>>

\usepackage{multirow}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{flow-chart.pdf}
  \caption{Flow chart for method to build RAX}
  \label{fig:flow-chart}
  \Description{Flow chart for method to build RAX}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{relationship.pdf}
  \caption{The relationship between score and CC}
  \label{fig:relationship}
  \Description{The relationship between score and CC}
\end{figure}

@@

Continue to collect other factors that may affect the evaluation of porting complexity,and select the following parameters through the Commit analyzer:architecture-related code lines, architecture-related files, and architecture keywords.
The number of architecture-related code lines and files is located using the keywords of X86, ARM, MIPS, RISCV, SPARC and other architectures.
Correlation comparison between Arch\_code and other factors acquired by Commit analyzer,as shown in Table \ref{tab:score}:

\begin{table*}
  \caption{The Spearman correlation coefficient of score and architecture-related factors}
  \label{tab:score}
  \begin{tabular}{cccccc}
    \toprule
    conditional compilation & Builtin & Intrinstic & syscall & asm & build\_scripts \\
    \midrule
    0.73 & 0.61 & 0.74 & 0.69 & 0.66 & 0.43 \\
  \bottomrule
\end{tabular}
\begin{tabular}{ccccc}
  \toprule
  time & authors & lines of arch & files of arch & keyword count \\
  \midrule
  -0.16 & 0.43 & 0.16-0.40 & 0.34-0.41 & 0.17-0.43 \\
\bottomrule
\end{tabular}
\end{table*}

@@

\begin{table}
  \caption{The Spearman correlation coefficient of score and architecture-related factors}
  \label{tab:evaluation}
  \begin{tabular}{ccccc}
    \toprule
     & Accuracy & Pmacro & Rmacro & F1macro \\
    \midrule
    Tool 1[26] & 0.838 & 0.802 & 0.880 & 0.823 \\
    RAX & 0.857 & 0.817 & 0.873 & 0.836 \\
  \bottomrule
\end{tabular}
\end{table}

@@

\begin{table}
  \caption{Effectiveness comparison chart}
  \label{tab:effectiveness}
  \begin{tabular}{ccccc}
    \toprule
     & \multicolumn{2}{c}{Tool 1} & \multicolumn{2}{c}{RAX} \\
     & TP & FN & TP & FN \\
    \midrule
    Low & 13 & 3 & 15 & 1 \\
    Medium & 5 & 2 & 5 & 2 \\
    High & 3 & 4 & 7 & 0 \\
    Sum & 21 & 9 & 27 & 3 \\
    project & \multicolumn{2}{c}{30} & \multicolumn{2}{c}{30} \\
  \bottomrule
\end{tabular}
\end{table}
